AIMS DataPlatform R Client Notebook Example

### 2019-08-26 docs/detailed-example.Rmd
Updates to examples

This example assumes you have stored an *AIMS DataPlatform API Key* in your `.Renviron` file.  See [here](index#usage-of-aims-dataplatform-api-key) to see what that means.

@@

The benefits to choosing a data series is that it comes from one location and parameter type, making the data easy to plot.  If we did not choose a data series from the *AIMS Weather* data set we might have to specify additional parameters to ensure the data is as expected.

@@

```{r}
results <- getAllData('10.25845/5c09bf93f315d', filters=list('series'=4067, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
```

@@

```{r}
results2 <- getData(aimsWeather, filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations", col='green')
lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")
```

>>>>

This example assumes you have obtained an *AIMS DataPlatform API Key*.  See [here](index#usage-of-aims-dataplatform-api-key) to see what that means.

@@

The benefits to choosing a data series is that it comes from one location and parameter type, making the data easy to plot.  If we did not choose a data series from the *AIMS Weather* data set we might have to specify additional parameters to ensure the data is as expected.  __Please note that in all code smaples below you should enter your own API Key in the field that says `my-api-key`.__

@@

```{r}
results <- getAllData('10.25845/5c09bf93f315d', apiKey='my-api-key', filters=list('series'=4067, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
```

@@

```{r}
results2 <- getAllData('10.25845/5c09bf93f315d', apiKey='my-api-key', filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-07'))
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations", col='green')
lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")
```
